---
title: "Coursera Presentation shinyapp"
author: "Menno Oerlemans"
date: "4 december 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
require(stats)
data(swiss)

```

## Introduction
- The shiny app was developed for the Developing data products course.  
- To build the app the swiss data from the stat package was used.  
- The shiny app can be accessed using the following link:  
https://mennooerlemans.shinyapps.io/Myfirstapp/  
- The documentation can be found using the following link:  
https://github.com/MennoOerlemans/Myfirstapp



## The data

- Data: Standardized fertility measure and socio-economic indicators for each of 47 French-speaking provinces of Switzerland at about 1888.
- The app is working on the swiss data:  
https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/swiss.html

The variables are:  
[,1]	Fertility	        Common standardized fertility measure  
[,2]	Agriculture	        % of males involved in agriculture as occupation  
[,3]	Examination	        % draftees receiving highest mark on army examination  
[,4]	Education	        % education beyond primary school for draftees.  
[,5]	Catholic	        % 'catholic' (as opposed to 'protestant').  
[,6]	Infant.Mortality	live births who live less than 1 year.  

## The app itself
- The app will give the plot of (a part of) the swiss dataset.  
- Fertility is used as the dependend  and the others as the explanatory variables.  
- The variable to be used as explanatory can be choosen in the dropbox in the side panel.  
- The plot is a scatterplot with all the points in the data (Fertility versus the choosen variable)  
- Under the plot the intercept and the slope of the lineair model are shown.  

## Plot of Agriculture

The full code can be found in: https://github.com/MennoOerlemans/Myfirstapp

The code for the plot is:

```{r echo=TRUE}
mf <- lm(Fertility ~ Agriculture, data = swiss)
plot(y = swiss$Fertility, x = swiss$Agriculture, ylab="Fertility", xlab="Agriculture", col="red")
abline(mf)
```

## Conclusion

The shiny application package is a usefull tool to present the results of a data study.

